Behavior Driven Development in Haskell

### 2012-05-28 paper.tex
typo fix.

Unfortunately, the type system of Haskell does not always guarantee
correct semantics.
For example, it does not ensure that division by zero does not occur.
Another example is lows of type classes. 
For instance, the {\tt Monad} class has three Monad lows 
that its instance \emph{should} satisfy
but
it is the programmers responsibility to ensure that
instance definitions \emph{behave} as \emph{expected}.

@@

In BDD, all behavior should be documented, together with some
\emph{evidence} for that behavior.
for this purpose, 
we brought a test method from other programming language community and
extended missing features.
In particular, we introduced Doctest~\cite{doctest} and
integrated it with QuickCheck~\cite{quickcheck}
for user documentation.
For code documentation, we also make use of Hspec inspired by RSpec~\cite{rspec}
and we proposed some combinators to it.

>>>>

Unfortunately, the type system of Haskell does not always guarantee
correct semantics.
For example, it does not ensure that division by zero does not occur.
Another example is laws of type classes. 
For instance, the {\tt Monad} class has three Monad laws 
that its instance \emph{should} satisfy
but
it is the programmers responsibility to ensure that
instance definitions \emph{behave} as \emph{expected}.

@@

In BDD, all behavior should be documented, together with some
\emph{evidence}\/s for that behavior.
for this purpose, 
we brought a test method from other programming language community and
extended missing features.
In particular, we introduced Doctest~\cite{doctest} and
integrated it with QuickCheck~\cite{quickcheck}
for user documentation.
For code documentation, we also make use of Hspec inspired by RSpec~\cite{rspec}
and we proposed some combinators to it.
